Plots for \enquote{Arrows for Parallel Computations}

### 2018-01-03 paper/separate_plots/main.tex
all relevant benchmarks added to separate plots pdf file, however scaling has still to be improved

\newcommand{\speedupplot}[7]{
\begin{tikzpicture}
\begin{axis}[title={#1},
title style={align=center},
scale only axis, width=#7,
xlabel=Threads,
%xtick=data,
%ytick=data,
xtick distance=#4,
ytick distance=#4,
ylabel=Speedup,
ylabel near ticks,
grid=major,
legend entries={linear, #2},
legend style={at={(0.01,0.99)},anchor=north west},
max space between ticks=50pt,
grid style={line width=.1pt, draw=gray!10},
major grid style={line width=.2pt,draw=gray!50},
ymin=-1,
xmin=-1,
ymax=#6,
xmax=#6]
\addplot [domain=0:#3, no markers,dotted,thick]{x};
#5
\end{axis}
\end{tikzpicture}
}

@@

@@

\meanOverheadPlot{Mean Overhead for distributed \\ \jacobitest 4253}{0.5}{32}{272}{\benchmarkDir/distributed-jacobi/3-4253-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for distributed \\ \jacobitest 3217}{0.5}{32}{272}{\benchmarkDir/distributed-jacobi/3-4253-diff.csv}

@@

@@

\speedupplot{Speedup of \rmtest \enquote{32}}{Eden CP, GpH, \ensuremath{\Conid{Par}} Monad}{16}{4}{
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/sm-rm/bench-sm-rm.bench.skelrm-parr-eden-cp-11213-32.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/sm-rm/bench-sm-rm.bench.skelrm-parr-mult-11213-32.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/sm-rm/bench-sm-rm.bench.skelrm-parr-par-11213-32.csv};
}{17}{\plotwidthSMP}

\speedupplot{Speedup of \rmtest \enquote{64}}{Eden CP, GpH, \ensuremath{\Conid{Par}} Monad}{16}{4}{
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/sm-rm/bench-sm-rm.bench.skelrm-parr-eden-cp-11213-64.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/sm-rm/bench-sm-rm.bench.skelrm-parr-mult-11213-64.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/sm-rm/bench-sm-rm.bench.skelrm-parr-par-11213-64.csv};
}{17}{\plotwidthSMP}

@@

\speedupplot{Parallel speedup of \sudokutest \enquote{1000}}{Eden CP, GpH, \ensuremath{\Conid{Par}} Monad}{16}{4}{
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/sudoku-sm/bench-sudoku-sm.bench.parrows-sudoku-parmap-eden-sudoku17.1000.txt.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/sudoku-sm/bench-sudoku-sm.bench.parrows-sudoku-parmap-mult-sudoku17.1000.txt.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/sudoku-sm/bench-sudoku-sm.bench.parrows-sudoku-parmap-par-sudoku17.1000.txt.csv};
}{17}{\plotwidthSMP}

@@

\speedupplot{Parallel speedup of \sudokutest \enquote{512}}{Eden CP, GpH, \ensuremath{\Conid{Par}} Monad}{16}{4}{
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/torus-sm/bench-torus-sm.bench.torus-matrix-parrows-eden-sm-512.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/torus-sm/bench-torus-sm.bench.torus-matrix-parrows-multicore-512.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/torus-sm/bench-torus-sm.bench.torus-matrix-parrows-parmonad-512.csv};
}{17}{\plotwidthSMP}

@@

>>>>

\newcommand{\speedupplot}[8]{
\begin{tikzpicture}
\begin{axis}[title={#1},
title style={align=center},
scale only axis, width=#7,
xlabel=Threads,
%xtick=data,
%ytick=data,
xtick distance=#4,
ytick distance=#4,
ylabel=Speedup,
ylabel near ticks,
grid=major,
legend entries={linear, #2},
legend style={at={(0.01,0.99)},anchor=north west},
max space between ticks=50pt,
grid style={line width=.1pt, draw=gray!10},
major grid style={line width=.2pt,draw=gray!50},
ymin=-1,
xmin=-1,
ymax=#8,
xmax=#6]
\addplot [domain=0:#3, no markers,dotted,thick]{x};
#5
\end{axis}
\end{tikzpicture}
}

@@

\speedupplot{Speedup of distributed \rmtest \enquote{44497 256}}{PArrows Eden}{256}{32}{
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/distributed-rm/bench-distributed.bench.skelrm-parrows-44497-256.csv};
}{272}{\plotwidthDist}{272}

@@

\meanOverheadPlot{Mean Overhead for distributed \\ \jacobitest 3217}{0.5}{32}{272}{\benchmarkDir/distributed-jacobi/3-4253-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for distributed \\ \jacobitest 4253}{0.5}{32}{272}{\benchmarkDir/distributed-jacobi/3-4253-diff.csv}

\speedupplot{Speedup of distributed \jacobitest \enquote{3217}}{PArrows Eden}{256}{32}{
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/distributed-jacobi/bench-jacobi.bench.jacobi-parr-3-4253.csv};
}{272}{\plotwidthDist}{272}

\speedupplot{Speedup of distributed \jacobitest \enquote{4253}}{PArrows Eden}{256}{32}{
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/distributed-jacobi/bench-jacobi.bench.jacobi-parr-3-4253.csv};
}{272}{\plotwidthDist}{272}

@@

\speedupplot{Speedup of distributed \torustest \enquote{4096}}{PArrows Eden}{256}{32}{
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/distributed-torus/bench-torus-distributed.bench.torus-matrix-parrows-eden-4096.csv};
}{272}{\plotwidthDist}{160}

@@

\speedupplot{Speedup of \rmtest \enquote{11213 32}}{Eden CP, GpH, \ensuremath{\Conid{Par}} Monad}{16}{4}{
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/sm-rm/bench-sm-rm.bench.skelrm-parr-eden-cp-11213-32.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/sm-rm/bench-sm-rm.bench.skelrm-parr-mult-11213-32.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/sm-rm/bench-sm-rm.bench.skelrm-parr-par-11213-32.csv};
}{17}{\plotwidthSMP}{17}

\speedupplot{Speedup of \rmtest \enquote{11213 64}}{Eden CP, GpH, \ensuremath{\Conid{Par}} Monad}{16}{4}{
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/sm-rm/bench-sm-rm.bench.skelrm-parr-eden-cp-11213-64.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/sm-rm/bench-sm-rm.bench.skelrm-parr-mult-11213-64.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/sm-rm/bench-sm-rm.bench.skelrm-parr-par-11213-64.csv};
}{17}{\plotwidthSMP}{17}

@@

\speedupplot{Parallel speedup of \sudokutest \enquote{1000}}{Eden CP, GpH, \ensuremath{\Conid{Par}} Monad}{16}{4}{
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/sudoku-sm/bench-sudoku-sm.bench.parrows-sudoku-parmap-eden-sudoku17.1000.txt.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/sudoku-sm/bench-sudoku-sm.bench.parrows-sudoku-parmap-mult-sudoku17.1000.txt.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/sudoku-sm/bench-sudoku-sm.bench.parrows-sudoku-parmap-par-sudoku17.1000.txt.csv};
}{17}{\plotwidthSMP}{17}

@@

\speedupplot{Parallel speedup of \sudokutest \enquote{512}}{Eden CP, GpH, \ensuremath{\Conid{Par}} Monad}{16}{4}{
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/torus-sm/bench-torus-sm.bench.torus-matrix-parrows-eden-sm-512.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/torus-sm/bench-torus-sm.bench.torus-matrix-parrows-multicore-512.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/torus-sm/bench-torus-sm.bench.torus-matrix-parrows-parmonad-512.csv};
}{17}{\plotwidthSMP}{17}

@@

\meanOverheadPlot{Mean Overhead for shared-memory \\ \torustest 512 vs Eden CP}{0.5}{4}{18}{\benchmarkDir/torus-sm/eden-cp-512-diff.csv}
